\documentclass[letterpaper,12pt]{article}



\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black
}
\usepackage[empty]{fullpage}
\usepackage{fancyhdr}
\usepackage{latexsym}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

% Use Times New Roman serif font (similar to Jake's resume)
\usepackage{times}
% Alternative serif options:
% \usepackage{mathptmx} % Times-like font with better math support
% \usepackage{charter} % Charter serif font
% \usepackage{palatino} % Palatino serif font

\setlength{\footskip}{4.4pt}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemLine}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \footnotesize #2 \\
      \textit{\small#3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingEdu}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \footnotesize #2 \\
      \textit{\small#3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubheadingLeadership}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \footnotesize #2 \\
      \textit{\small#3} & \textit{\footnotesize #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-1pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{center}
    \textbf{\huge Joseph Telaak} \\ \vspace{6pt}
    704-351-7396 $|$ \href{mailto:jttelaak04@gmail.com}{\underline{jttelaak04@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jtelaak/}{\underline{linkedin.com/in/jtelaak}}
\end{center}

%-----------EDUCATION-----------------
\vspace{1pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingEdu
      {University of South Carolina}{Columbia, SC}
      {BSE in Computer Engineering, Leadership Distinction in Research (GPA: 3.61)}{Aug. 2022 -- Dec. 2024}
    
    % \resumeSubheadingEdu
    %   {South Carolina Governor's School for Science and Mathematics (SCGSSM)}{Hartsville, SC}
    %   {High School Diploma, Concentration in CS and Math}{Aug. 2020 - May 2022}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\vspace{1pt}
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Chief Executive Officer}{Dec. 2024 - Present}
      {Parkeze Inc.}{Columbia, SC}
      \resumeItemListStart
        \resumeItemLine{Led end-to-end development of ultra-low-power IoT parking sensors, from concept to market launch.}
        \resumeItemLine{Architected cloud-native backend infrastructure supporting real-time data streaming to 1000+ users.}
        \resumeItemLine{Optimized sensor hardware and firmware achieving 120\% power reduction and 300\% cost savings.}
        \resumeItemLine{Built comprehensive analytics platform using React, GraphQL, and TimescaleDB for data insights.}
        \resumeItemLine{Implemented a highly extensible event ingestion and emission pipeline using Kafka to support 3rd-party systems.}
        \resumeItemLine{Developed several extensions for Keycloak's open-source IAM to support our unique authorization requirements.}
        \resumeItemLine{Created a CI/CD pipline to perform end-to-end integration testing and blue/green deployment on Kubernetes.}
        \resumeItemLine{Ported the LoRaWAN gateway stack to Zephyr RTOS with custom high-availabilty features for our gateways.}
        \resumeItemLine{Involved in all aspecrts of the business, including fundraising, sales, marketing, and customer support.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Research Assistant}{Feb. 2023 - Dec. 2024}
      {USC Systems Research on X Lab}{Columbia, SC}
      \resumeItemListStart
        \resumeItemLine{Co-authored research on novel mmWave radar algorithms for 3D vehicle and pedestrian detection.}
        \resumeItemLine{Secured research funding through competitive grant proposals.}
        \resumeItemLine{Developed contactless vital sign monitoring system.}
        \resumeItemLine{Designed data collection infrastructure supporting multiple research projects.}
      \resumeItemListEnd

    \resumeSubheading
      {Project Lead}{Jan. 2022 - Feb. 2023}
      {SCGSSM Autonomous Golf Cart}{Hartsville, SC}
      \resumeItemListStart
        \resumeItemLine{Transformed a standard golf cart into an autonomous vehicle platform for research.}
        \resumeItemLine{Engineered a complete ADAS control module for the golf cart's steering, throttle, and braking systems.}
        \resumeItemLine{Designed custom Nvidia Jetson carrier board with multi-channel analog-to-digital video capture capabilities.}
        \resumeItemLine{Implemented computer vision pipeline for obstacle detection, traffic sign recognition, and lane tracking.}
        % \resumeItemLine{Mentored 20+ students and established ongoing curriculum for autonomous systems development.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Research Assistant}{Summer 2021}
    %   {USC Cyberinfrastructure Lab}{Columbia, SC}
    %   \resumeItemListStart
    %     \resumeItemLine{Automated equipment configuration, throughput testing, and packet loss measurements in networks.}
    %     \resumeItemLine{Created an on-switch webserver load balancer in P4.}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------VOLUNTEERING-----------------
\vspace{1pt}
\section{Leadership}
  \resumeSubHeadingListStart
    % \resumeSubheadingLeadership
    %   {SCGSSM Board of Directors}{Hartsville, SC}
    %   {Alumni Association Engagement Committee Member}{Jul. 2023 - Present}
    \resumeSubheadingLeadership
      {FIRST Robotics}{Columbia, SC}
      {FIRST Technical Advisor, Judge, Robot Inspector}{Jan. 2022 - May 2025}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\vspace{1pt}
\section{Selected Projects}
  \resumeSubHeadingListStart

    \resumeSubItem{PiSwitch}
      {Created a 7-port router/network switch with custom controller, web UI, and out-of-band management.}

    \resumeSubItem{LLM Voice Assistant}
      {Designed a far-field mic array with XMOS DSP, Zephyr on i.MXRT, ESP32 Wi-Fi NIC, OTA for all 3 major chips, and real-time audio streaming to a LLM pipeline.}

    \resumeSubItem{Agentic Audio Streamer}
      {Developed a multi-room audio streaming system using an SigmaDSP, DACs, and Raspberry Pi CM5. Integrated Spotify Connect and enabled external control via a custom API for LLMs.}

    \resumeSubItem{RISCv CPU}
      {Implemented a parallelized RISCv CPU with GPIO on an FPGA.}

    % \resumeSubItem{Rocket Flight Computer}
    %   {Arduino flight computer with GPS, IMU, barometer, and LoRa telemetry on custom PCB.}

    \resumeSubItem{Pick-n-Place Machine}
      {Designed and built a desktop PCB assembler running Marlin and OpenPNP.}

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\vspace{1pt}
\section{Skills}
 \resumeSubHeadingListStart
   \resumeSubItem{Software}{C/C++, Python, Java, MATLAB, Rust, LUA}
   \resumeSubItem{Tooling}{Altium, KiCad, Quartus, STM32 Cube, MXUExpresso, mmWave Studio}
   \resumeSubItem{Embedded}{Zephyr, Yocto, Buildroot}
   \resumeSubItem{Memberships}{IEEE Eta Kappa Nu (HKN), IEEE MTTS, IEEE, ACM, AIAA}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}